Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-03 p2/works-inverse.tex
Simpler theorem for common heads

\begin{mylem}\label{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these (as $\worksmeqsign$ is transitive)
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.

>>>>

\begin{mylem}\label{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}

TODO WHY NOT: See \cref{combine_independent_sequences}
\[ B\indep C \Rightarrow \worksmbb{A\cc B, A\cc C}{A\cc B\cc C} \]

\end{mylem}
\begin{proof}

TODO NEW PROOF:

TODO OLD PROOF:

Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these (as $\worksmeqsign$ is transitive)
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.
